\large{McGill University | Desautels Faculty of Management}\\ \hfill \break \hfill \break \hfill \break \hfill \break \\\Large MGSC 670 - Revenue Management\\ \textbf{Group Assignment 1: Markdown Strategy}\\ \hfill \break \hfill \break

### 2023-05-15 manuscript/manuscript.tex
added plots and latex

\subsection{Data Treatment}

\subsection{Simulation}

>>>>

\subsection{Data Treatment}
While we have access to 15 runs of “historical” data, before using this data, we must apply data preprocessing.

First, we must ensure that the data does not contain errors or null values. 
We, therefore, removed null rows and appended the run number (1-15) to each observation within the data. 
After the data cleanup, we are left with a dataset containing the run number, the week number, the price of the item (\$60, \$54, \$48, \$36), the unit demand and the revenue generated from that week of sales.

Second, we need to transform the data into more meaningful formats. 
We grouped the data by price to measure unit sales’ standard deviation and mean. 
This first grouping was helpful in the naïve price policy we applied. 
We also grouped the data by price to measure the mean and standard deviation of the unit sales compared to the previous week. 
In other words, what is the \% increase (or decrease) in unit sales when a new price point is set. It may be that a 20\% decrease in price increases unit sales by 70\%, independent of the previous price point.

Based on some casual observations of the data, the distributions appear roughly normally distributed, we will use this as a basis for simulation and modelling.

\subsection{Simulation}
To forecast the impact of the pricing strategies we are investigating, we must test the policies against data. 
Since we cannot access the exact equation or similar random number generator used for the web app, we must first utilize simulations. 
The model built takes the policy, the average and the standard deviation of the observed price points and generates 100 simulations. 
For each simulation and each time t, the model generates unit sales based on a numpy random normal method using the mean and standard deviation of the current price point. 
The simulation approach best reflects a real-life scenario as a forecast function is generally unknown, resulting in a reliance on past data to predict future demand. 
The generated numbers reflect the data distribution found within the historical data.

\subsection{Validation}
The simulation approach helps validate the models and quickly select the best policy with limited information. 
However, for this context, we need not rely solely on the simulation data, we can instead use the actual data from the web app. 
The assumptions and approach we have previously laid out may have unknown challenges or other pitfalls. 
In this scenario we are not limited to the simulation and approximation of “real world data”. 
We will therefore validate the simulation results using the web application. 
To implement the validation, we will utilize a selenium-based python script which goes between the code and user interface on the web app. 
Each policy is tested in real-time against the app while recording the results to evaluate after the fact.
